\documentclass[oneside]{book}

\setcounter{tocdepth}{1} 
\setcounter{secnumdepth}{2} 

\usepackage{amsmath, amsthm}
\theoremstyle{plain}
\newtheorem{theo}{Theorem}%[section] 
\newtheorem{lem}[theo]{Lemma}
\theoremstyle{definition}
\newtheorem{defn}[theo]{Definition}
\theoremstyle{remark}
\newtheorem{rmk}[theo]{Remark}

\newtheoremstyle{mystyle}% name
{3pt}% space above
{3pt}% space below
{}% body font
{}% indent amount
{}% theorem head font
{.}% punctuation after theorem head
{.5em}% space after theorem head
{}% theorem head spec

\theoremstyle{mystyle}
\newtheorem{exc}[theo]{Exercise}

\begin{document}

\paragraph{An initial paragraph} at the top ...

\chapter{Intro}
This is the introduction.

\chapter{Background}
This is the background.

\chapter{Counters}
%\renewcommand{\thetheorem}{\alph{theorem}}
\begin{itemize}
\item {\tt chapter}: \thechapter, \roman{chapter}
\item {\tt section}: \thesection, \roman{section}
\item {\tt subsection}: \thesubsection, \roman{subsection}
\item {\tt theorem}: \thetheo, \roman{theo}
\item {\tt equation}: \theequation, \roman{equation}
\end{itemize}

%--------------------
\section{Numbered lists}
\renewcommand{\theenumii}{\Alph{enumii}}
\begin{enumerate}
\item (\theenumi, \theenumii)
    \begin{enumerate}
    \item (\theenumi, \theenumii)
    \item (\theenumi, \theenumii)
    \end{enumerate}
\item (\theenumi, \theenumii)
    \begin{enumerate}
    \item (\theenumi, \theenumii)
    \item (\theenumi, \theenumii)
    \item (\theenumi, \theenumii)
    \end{enumerate}
\item (\theenumi, \theenumii)
    \begin{itemize}
    \item (\theenumi, \theenumii)
    \item (\theenumi, \theenumii)
    \end{itemize}
\item (\theenumi, \theenumii)
\end{enumerate}

%--------------------
\section{Internal counters}
These do not have corresponding {\tt thecounter} commands.
\begin{itemize}
\item {\tt tocdepth}: \arabic{tocdepth}
\item {\tt secnumdepth}: \arabic{secnumdepth}
\end{itemize}

%--------------------
\section{Paragraphs}
The {\tt paragraph} and {\tt subparagraph} counters are only incremented if {\tt secnumdepth} is set to 4 and 5 respectively.

\setcounter{secnumdepth}{5} 

\subsection{SS Title}
%\subsubsection{SSS Title}

\paragraph{First paragraph} blah blah
\subparagraph{First subparagraph} blah blah

\begin{itemize}
\item \theparagraph\ blah %, \arabic{paragraph}
\item \thesubparagraph\ blah blah %, \arabic{subparagraph}
\end{itemize}

\paragraph*{This is a starred paragraph.} We can reset {\tt theparagraph}, to {\tt Alph} here ...
\renewcommand{\theparagraph}{\Alph{paragraph}}

\paragraph{Second paragraph} blah blah
\subparagraph{Second subparagraph} blah blah

%--------------------
\section{Theorems}

%\alph{section}
%\thesection
%
%\renewcommand{\thesection}{\thechapter.\alph{section}}
%\thesection
%
%\renewcommand{\thesection}{\alph{chapter}.\alph{section}}
%\thesection

\begin{defn}
This is a definition
\end{defn}

\begin{lem}
This is a lemma
\end{lem}

\begin{theo}
This is a theorem.
\begin{proof}
This is a proof
\end{proof}
\end{theo}

\subsection{Some remarks}

\begin{rmk}
This is a remark.
\end{rmk}

\begin{exc}
This is an exercise.
\end{exc}

\alph{chapter}

\thechapter


\end{document}
